Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation

### 2014-11-14 conclusion.tex
intro spell check
red thing

In this paper, we have proposed a method for generating 3D CAD model
exemplar detector templates on-the-fly, based on a novel variant of
WHO features called NZ-WHO. As it circumvents the need for
calibration, it is computationally efficient, allowing it to be run in
an on-the-fly setting. As a result, we can use our method to enrich
existing object class detections with additional information such as
precise 3D pose and 3D CAD model exemplar.

>>>>

We have proposed a method for generating 3D CAD model
exemplar templates on-the-fly, based on a novel variant of
WHO features (NZ-WHO). It circumvents the need for
calibration, is computationally efficient, and allows it to be run in
an on-the-fly setting. As a result, we can use our method to enrich
existing object detections with additional information such as
precise 3D pose and 3D CAD model exemplar. Combined with an R-CNN
detector, we achieve state-of-the-art
results in joint detection and VP estimation.
